Peptide retention time prediction

### 2015-10-07 retention.tex
some new answers

The available technologies to infer peptides and proteins from mass
spectrometry data involve predicting the the potential manifestations
of the analyzed peptides, such as their fragmentation pattern, and
comparing those predicted properties to the observed data. Such
comparisons are regularly done for discovery proteomics by search
engines. However, an attractive way to increase the sensitivity of the
inference procedure is to also predict properties such as their
iso-electric point~\cite{branca2014hirief} or of particular interest
for this review, chromatographic retention
time \cite{cerqueira2010mude}.

>>>>

The available technologies to infer peptides and proteins from mass
spectrometry data involve predicting the the potential manifestations
of the analyzed peptides, such as their fragmentation pattern, and
comparing those predicted properties to the observed data. Such
comparisons are regularly done for discovery proteomics by search
engines. However, an attractive way to increase the sensitivity of the
inference procedure is to also predict properties such as their
iso-electric point~\cite{perez2011silico,branca2014hirief} or of
particular interest for this review, chromatographic retention time
\cite{cerqueira2010mude}. One way to determie a predicatble sparation
techniques usefulness is to estimate its ability to remove candidate
peptides of any detected feature, normally measured by a false
positive ratio (FPR), also known as the methods fall-out. Current
retention time prediction algorithms have an FPR of about
$\frac{1}{5}$, meaning that it can remove about four out of five
candidate peptides for a given feature. This could be compared to the
FPR of about $\frac{1}{200}$ for predictions of high-resolution
iso-electric focusing experiments~\cite{branca2014hirief}. The
retention time prediction have toimprove quite a bit to come to level
with the fall-out of iso-electric focusing, however, almost all mass
spectrometry-based proteomics use reversed phase chromatography, while
very few studies are using iso-electric focusing.

% An estimate of a FPR for MS1's would be great here.
